Benchmarking neuromorphic systems with Nengo

### 2015-07-28 paper/paper.tex
Add comment about speed and passthrough nodes

Other backends also incur overhead,
especially when data is recorded
through probes.
We investigated the possibility
that the overhead involved in probes
dominated the actual run time for some backends.
However, we found that
removing probes from these models
made very little impact on
the total time taken in a \texttt{run} call
(see Supplementary Figure~1).

>>>>

Interestingly, while removing passthrough nodes
results in significantly slower run times
for the reference backend,
it speeds up the OpenCL and SpiNNaker backends slightly.
This result indicates that passthrough nodes
add to the overhead incurred by
SpiNNaker and OpenCL.
Other backends also incur overhead,
especially when data is recorded
through probes.
We investigated the possibility
that the overhead involved in probes
dominated the run time for some backends.
However, we found that
removing probes from these models
made very little impact on
the total time taken in a \texttt{run} call
(see Supplementary Figure~1).
